### 2014-02-23 paper/retrofit.tex
expand scheduling policies; sequential is not right; wip

\begin{figure}
  Round robin:
\begin{code}
  sched step (it1, it2, ...)    = it2, ..., it1
  sched noStep (it1, it2, ...)  = it2, ...
  sched fork                    = sched step
\end{code}
  Browbound:
\begin{code}
  sched step                    = Id
  sched noStep (it1, it2, ...)  = it2, ...
  sched fork                    = Id
\end{code}
  Sequential:
\begin{code}
  sched step                       = Id
  sched noStep (it1, it2, ...)     = Id
  sched fork (it1, it2, ... it1n)  = itn, t1, t2, ...
\end{code}
\caption{scheduling policies}
\end{figure}

>>>>

\begin{figure}
  Round robin:
\begin{code}
  sched step (it1, it2, ...)    = it2, ..., it1
  sched noStep (it1, it2, ...)  = it2, ...
  sched fork (it1, it2, ...)    = it2, ..., it1
\end{code}
  Browbound:
\begin{code}
  sched step (it1, it2, ...)    = it1, it2, ...
  sched noStep (it1, it2, ...)  = it2, ...
  sched fork (it1, it2, ...)    = it1, it2, ...
\end{code}
  Sequential:
\begin{code}
  sched step (it1, it2, ...)       = it1, it2, ...
  sched noStep (it1, it2, ...)     = it1, it2, ...
  sched fork (it1, it2, ... it1n)  = itn, it1, it2, ...
\end{code}
\caption{scheduling policies}
\end{figure}
